\section{Academic Employment \& Affiliations}
\subsection{Current}
\cvline{Since 10/2021}{\textbf{University of Bern} \newline{}
Postdoctoral researcher at the \href{https://www.ipw.unibe.ch/index_eng.html}{\textit{Institute of Political Science}}, affiliated with the \href{https://www.oeschger.unibe.ch/}{\textit{Oeschger Center for Climate Change Research} (OCCR)}. Working in the research consortia \href{www.sweet-sure.ch}{SWEET SURE} (SUstainable and Resilient Energy for Switzerland) with a focus on trade-offs between energy pathways and shocks using serious games \& \href{www.sweet-edge.ch}{SWEET EDGE} (Enabling Decentralized renewable GEneration in the Swiss cities, midlands, and the Alps) focusing on the public acceptance of domestic renewable energy generation and international climate policies. %, both funded by the Swiss Federal Office of Energy, SFOE.
} 

\subsection{Previous}
\cvline{09 - 12/2023}{\textbf{London School of Economics and Political Science (LSE)}\newline{} Visiting Fellowship at the \href{https://www.lse.ac.uk/social-policy}{Department of \textit{Social Policy}} \& \href{https://www.lse.ac.uk/granthaminstitute/}{\textit{Grantham} Research Institute on Climate Change and the Environment}.} %Research project on urban environmental policies.} 
\cvline{10/2017 - 09/2021}{\textbf{ETH Zurich} \newline{} Researcher and PhD candidate at the \href{https://ib.ethz.ch/}{\textit{International Political Economy and Environmental Politics}} group \& the \href{https://istp.ethz.ch/}{\textit{Institute of Science, Technology and Policy}}% (Swiss Mobility Lab). Projects included \textit{Fostering the Transition Towards More Fuel-Efficient Cars}
.} 


\section{Completed Education}
 \cvline{2017 – 2021}{ \textbf{Dr. sc. ETH}, ETH Zurich, Switzerland
  \newline{}%\textbf
  {Thesis:} \textit{Electric vehicle adoption and acceptance}\newline{}Supervisor: Prof. Dr. Thomas Bernauer
  \newline{} Committee: Prof. Dr. Isabelle Stadelmann-Steffen, Prof. Dr. Kay W. Axhausen}

 \cvline{2014 – 2017}{ \textbf{Master of Science International Economics and Policy Consulting}, University of Magdeburg, Germany 
  \newline{%\textbf
  {Thesis:} \textit{An Econometric Analysis of the Effect of Political Contributions from the Oil Industry on Votes at the US Congress}}} 

 \cvline{2015 – 2016}{University of Nice Sophia Antipolis, {Erasmus Scholarship}, Nice, France}

 \cvline{2010 – 2013}{ \textbf{Bachelor of Science Economics}, Ludwig-Maximilians University (LMU), Munich, Germany
  \newline{%\textbf
  {Thesis:} \textit{Widowhood, Medical Expenditures, and Health Care Utilization among the Elderly US Population}}}
 \cvline{2012 – 2013}{Stockholm University, {Erasmus Scholarship}, Stockholm, Sweden}
  \cvline{2010}{Abitur, Roßleben, Germany}