\section{List of Academic Presentations}
 \subsection{Conference \& academic workshop presentations}
  \cvline{2025}{\textbf{SPSA} (Swiss Political Science Association Annual Congress) (as presenter and panel organiser), \textbf{ALPOP}, Annual Meeting \textbf{Methods of Political Science Research Section DVPW} (German Political Science Association), \textbf{PolMeth Europe}, \textbf{EPG} (Environmental Politics and Governance) survey workshop, \textbf{3SHE} (Swiss Social Science and Humanities Energy) Workshop, EPSA (accepted).} 
  \cvline{2024}{\textbf{SPSA}, \textbf{APSA} (American Political Science Association) \textbf{Virtual Research Meeting} (as presenter and panel organiser), \textbf{3SHE} Workshop, \textbf{EPSA} (European Political Science Association Annual Congress), \textbf{E4EE} (Workshop on Experimental Economics for the Environment).}
 \cvline{2023}{\textbf{SPSA}, \textbf{EPCS} (European Public Choice Society), \textbf{EPSA}, \textbf{3SHE} Workshop (as organiser and presenter), \textbf{Dreiländertagung} %(D-A-CH Congress)
 (as presenter and panel organiser).}
 \cvline{2022}{\textbf{SPSA}, \textbf{PolMeth Europe}, two \textbf{3SHE} workshops (lead organiser), \textbf{EPSA}, \textbf{EPG} online.}
 \cvline{2021}{\textbf{SPSA}, \textbf{OSWEET} (Online Summer Workshop in Environment, Energy, and Transportation).}
\cvline{2020}{EMEE, SPSA (both accepted, not participated due to injury). \textbf{PSA ECN} (Political Studies Association, Early Career Network). %{3-Länder International Political Economy} (Paper accepted, conference cancelled.)
}
\cvline{2019}{\textbf{IAEE} (International Association of Energy Economics) International Conference, \textbf{EPSA}, \textbf{AIEE} (Italian affiliate of IAEE) Energy Symposium.}

\subsection{Invited talks \& seminar presentations}
\cvline{2025}{University of Konstanz, Department of Politics and Public Administration, Center for Data and Methods Colloquium.}
\cvline{2024}{ECPR Methodology Section -- ECR Virtual Seminar Series on Survey Research.}
 \cvline{2023}{London School of Economics and Political Science, Social Policy Research Seminar.}
 \cvline{2023}{University of Lausanne \& EPFL CLIMACT (Center for Climate Impact and Action) Seminar.}
  \cvline{2023}{SWEET EDGE Biennial Conference, Bern.}
   \cvline{2021}{UC Davis, California, Institute of Transportation Studies, Plug-in Hybrid and Electric Vehicle Research Center, Seminar.}
      \cvline{2021}{University of Bath, Environment, Transport, and Sustainability (EnTS) Research.}
                  \cvline{2021}{Z-PESS (Zurich Political Economy Seminar Series).}