%%% Teaching Experience ___________________________________________________________________________________________________________________________________________________
\section{Teaching \& Supervision}

\cvline{\textit{(Note:}}{${\mathbb{B}}$ \textit{denotes teaching for Bachelor's students,} ${\mathbb{M}}$ \textit{for Master's students, and ${\mathbb{P}}$ for PhD students. The course language was English unless} ${\timesbf{G}}$ \textit{indicates courses in German.)}}

\subsection{Own semester-long teaching}
\cvline{Since 2022 (annually)}{\textbf{Seminar} \textit{Energy and Mobility Policies for Decarbonisation} $^{(\mathbb{M})}$, \newline{}University of Bern.}
%\cvline{2024}{\textbf{Lecture} \textit{Die Kunst der kausalen Inferenz} (The Art of Causal Inference), University of Bern.}
%Syllabus Link: https://brueckmann.github.io/KKI_Syllabus/PDF_Syllabus_KKI_GBrueckmann.pdf
\cvline{2024}{\textbf{Lecture} \textit{The Art of Causal Inference} $^{(\mathbb{B} \& \mathbb{M},\timesbf{G})}$, University of Bern.}
\newpage
\subsection{Co-teaching \& guest lectures}
\cvline{2024}{\textbf{Guest lecture} \textit{Renewable Energy Acceptance using Causality and Data Science} in Domain Experience: Data analytics for energy systems and IOT $^{(\mathbb{M})}$ \newline{} Organiser: P. Schütz, Lucerne University of Applied Sciences and Arts.}
\cvline{2023}{\textbf{Lectures} \textit{Political Economy of Climate Change} $^{(\mathbb{M} \& \mathbb{P})}$ \newline{} Organiser: V. Koubi, University of Bern.}
\cvline{2023}{\textbf{Guest lecture} \textit{Acceptance of Electric Vehicle Policies} in Topics on Advanced Transport Engineering $^{(\mathbb{M})}$ Organiser: Namibia University of Science \& Technology.}
\cvline{2022}{\textbf{Guest lecture} \textit{Climate Change Policy and Electric Vehicles in Europe} in Climate Physics Seminar $^{(\mathbb{B} \& \mathbb{M})}$ Organiser: Weber State University, Ogden, Utah.}
\cvline{2021}{\textbf{Seminar} \textit{Battery-electric vehicle adoption and RCTs} 
in Frontiers in Energy Research $^{(\mathbb{P})}$ Organiser: Energy Science Centre, ETH Zurich.}
\cvline{2021}{\textbf{Lecture} \textit{Sustainable Development} in \textit{Political Economy} $^{(\mathbb{M} \& \mathbb{P})}$ \newline{} Organiser: Organised with V. Koubi \& D. Kolcava, ETH Zurich.}
\cvline{2020}{\textbf{Lecture} \textit{Experimental Political Science} in Proseminar 2 $^{(\mathbb{B} \& \mathbb{M},\timesbf{G})}$ \newline{} Organisers: D. Presberger, F. Quoß, ETH Zurich.}
\cvline{2018, 2019}{\textbf{Tutorial} \textit{Empirical Social Science Research Methods} $^{(\mathbb{B},\timesbf{G})}$ \newline{} Organiser: L. Rudolph, ETH Zurich.}
%\textit{Methoden der Empirischen Sozialforschung}
\cvline{2018, 2019}{\textbf{Seminar} \textit{The Mobility Challenge} in \href{https://idealeague.org/students/challenge-programme}{IDEA League Challenge programme} $^{(\mathbb{B} \& \mathbb{M})}$ \newline{} Organiser: T. Bernauer, ETH Zurich.}
%\cvline{2012}{\textbf{Tutorial} \textit{Mathematische Methoden der VWL} (mathematical methods in economics), LMU Munich.}
\cvline{2012}{\textbf{Tutorial} \textit{Mathematical Methods in Economics} $^{(\mathbb{B},\timesbf{G})}$, LMU Munich.}


\subsection{Supervision \& examinations}
\cvline{2024}{\textbf{Pre-doc examination} (committee member), Renewable Energy Systems, Organiser: Prof. Dr. Evelina Trutnevyte, University of Geneva.}
\cvline{Since 2021}{\textbf{Mentoring} PhD students at the Institute of Political Science and the Oeschger Centre for Climate Change Research, University of Bern.}
\cvline{2021}{\textbf{Supervision of Master's thesis} \textit{Electric charging behaviour – Understanding the trilemma of willingness to pay, the value of time and source of energy in the context of public charging stations in the German part of Switzerland}, ETH Zurich.}
\cvline{2020}{\textbf{Supervision of Master's thesis} \textit{The role of charging infrastructure to the mainstream adoption of battery electric vehicles (BEVs)}, ETH Zurich.}