%%% Funding ___________________________________________________________________________________________________________________________________________________
%\section{Awards and Funding}
\section{Funding \& Grants received (\textSum{} CHF 57,200)}
\cvline{2025}{\textbf{Goethe University} \textit{travel grant} for the ``Publishing International Political Economy'' Workshop
($\textstyle{\approx}$ CHF 187).} % 200 Euro
\cvline{2025}{\textbf{University of Bern} \textit{in-kind grant} for a research assistant for 8 months awarded by the Faculty of Business, Economics and Social Sciences, \textit{competitive funding scheme for young researchers with outstanding scientific qualifications}($\textstyle{\approx}$ CHF 17,500).}
% 270 Euro 
\cvline{2025}{\textbf{MZES} \textit{travel grant} for the MZES-DVPW Conference ``Methods of Political Science'' ($\textstyle{\approx}$ CHF 250).}
\cvline{2024}{\textbf{University of Bern} \textit{in-kind grant} for a teaching assistant for the fall 2024 Master's seminar, awarded by the \textit{eCoaches for digital skills in teaching} programme ($\textstyle{\approx}$ CHF 11,500).}
\cvline{2023}{\textbf{Berne University Research Foundation} \textit{travel grant} for research stay at London School of Economics and Political Science (CHF 3,398).} %until here everything adds up to 27898
\cvline{2023}{\textbf{Swiss Academy of Social Sciences and Humanities} \textit{travel grant} for Dreiländertagung, Linz, Austria (CHF 500).}
\cvline{2023}{\textbf{UniBE Short Travel Grants for (Post)Docs} \textit{travel grant} for research stay at London School of Economics and Political Science (CHF 7,000).}
\cvline{2022}{\textbf{Swiss Academy of Social Sciences and Humanities} \textit{project funding} for Swiss Social Science and Humanities Energy Research Group (CHF 7,000).}
\cvline{2022}{\textbf{Swiss Office of Energy (SFOE)} \textit{project funding} for Swiss Social Science and Humanities Energy Research Group Workshops (CHF 5,000).}
\cvline{2022}{\textbf{Fund for the Promotion of Young Researchers} \textit{project funding} for Swiss Social Science and Humanities Energy Research Group Workshops, jointly received with R. Sträter and J. Schmid (CHF 5,000).}

% \subsection{older Academic Awards and Scholarships}
% \cvline{2017}{\textit{Dean’s List of Excellent Alumni}, Faculty of Economics and Management, University of Magdeburg}
% \cvline{2011 - 2013}{Invitation to participate in \textit{Munich Honours Program in Economics}}
% \cvline{2008 - 2011}{Scholarship \textit{Studienkompass} from SDW}
% \cvline{2010}{Awards from Siemens, German Mathematicians Society, and German Chemistry Society}
% \cvline{2008 - 2010}{Scholarship POK Pühringer Privatstiftung, Vienna}
